---
title: "Investment Plan"
subtitle: "Global Allocation Roadmap — September 2026"
date: today
format:
  html:
    theme: cosmo
    embed-resources: true
    toc: true
    toc-depth: 2
    toc-title: "On This Page"
    fig-width: 9
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(gt)
library(scales)

# ── Data ──────────────────────────────────────────────────────────────────────
signals  <- read_csv("outputs/tables/2026-09-21_indicator_signal_dashboard.csv",
                     show_col_types = FALSE)
cop_rank <- read_csv("outputs/tables/2026-09-21_cop_vehicle_ranking.csv",
                     show_col_types = FALSE)
alloc    <- read_csv("outputs/tables/2026-09-21_ranked_allocation_recommendation.csv",
                     show_col_types = FALSE)
country  <- read_csv("data/processed/country_opportunity_screen_20260921.csv",
                     show_col_types = FALSE)
theme_sc <- read_csv("data/processed/theme_opportunity_screen_20260921.csv",
                     show_col_types = FALSE)

# ── Constants ─────────────────────────────────────────────────────────────────
MONTHLY_INVEST  <- 5200     # Monthly contribution to self-directed brokerage (Fidelity/Schwab)
COP_GAP_USD     <- 19600    # Spending-based COP reserve target (base: 18-month coverage)
MONTHS_TO_CLOSE <- 4        # Months at $5,200/mo to fund COP spending reserve
USD_NW          <- 557994
LIQUID          <- 309908

# ── Palette ───────────────────────────────────────────────────────────────────
CLR_NAVY  <- "#1e3a5f"
CLR_GREEN <- "#4a9e7a"
CLR_AMBER <- "#c97d25"
CLR_RED   <- "#c94040"
CLR_GRAY  <- "#6c757d"
```

```{=html}
<style>
.kpi-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(175px, 1fr));
  gap: 1rem;
  margin: 0.5rem 0 2rem 0;
}
.kpi-card {
  background: #f8f9fa;
  border-left: 4px solid #1e3a5f;
  border-radius: 6px;
  padding: 1.1rem 1.3rem 0.9rem;
}
.kpi-value {
  font-size: 1.55rem;
  font-weight: 700;
  color: #1e3a5f;
  line-height: 1.1;
}
.kpi-label {
  font-size: 0.72rem;
  color: #6c757d;
  text-transform: uppercase;
  letter-spacing: 0.06em;
  margin-top: 0.3rem;
}
.kpi-sub {
  font-size: 0.78rem;
  color: #adb5bd;
  margin-top: 0.2rem;
}
.kpi-card.green { border-left-color: #4a9e7a; }
.kpi-card.green .kpi-value { color: #4a9e7a; }
.kpi-card.amber { border-left-color: #c97d25; }
.kpi-card.amber .kpi-value { color: #c97d25; }
.kpi-card.red   { border-left-color: #c94040; }
.kpi-card.red   .kpi-value { color: #c94040; }
.note-box {
  background: #f0f7f4;
  border-left: 4px solid #4a9e7a;
  border-radius: 4px;
  padding: 0.75rem 1rem;
  font-size: 0.88rem;
  margin: 1rem 0;
}
.warn-box {
  background: #fff8f0;
  border-left: 4px solid #c97d25;
  border-radius: 4px;
  padding: 0.75rem 1rem;
  font-size: 0.88rem;
  margin: 1rem 0;
}
.phase-header {
  background: #1e3a5f;
  color: white;
  padding: 0.6rem 1rem;
  border-radius: 4px;
  font-weight: 600;
  font-size: 1rem;
  margin: 1.25rem 0 0.75rem;
}
hr { border-color: #dee2e6; margin: 2rem 0; }
</style>
```

## Situation Summary {.unnumbered}

::: kpi-grid
<div class="kpi-card amber">
<div class="kpi-value">97.4% USD</div>
<div class="kpi-label">Current Currency Mix</div>
<div class="kpi-sub">Target: spending-based COP reserve</div>
</div>
<div class="kpi-card red">
<div class="kpi-value">~$10K gap</div>
<div class="kpi-label">COP Reserve Shortfall</div>
<div class="kpi-sub">Target ~$19.6K (18-mo spending base)</div>
</div>
<div class="kpi-card">
<div class="kpi-value">$5,200/mo</div>
<div class="kpi-label">Investment Capacity</div>
<div class="kpi-sub">Self-directed brokerage (Fidelity/Schwab)</div>
</div>
<div class="kpi-card green">
<div class="kpi-value">~4 months</div>
<div class="kpi-label">COP Reserve Build</div>
<div class="kpi-sub">Then begin 7-class global portfolio</div>
</div>
<div class="kpi-card green">
<div class="kpi-value">5.7%</div>
<div class="kpi-label">Colombia TES Real Yield</div>
<div class="kpi-sub">Fisher-adjusted, USD investor</div>
</div>
<div class="kpi-card">
<div class="kpi-value">3.75</div>
<div class="kpi-label">Top ETF Conviction (INDA)</div>
<div class="kpi-sub">India; out of 5.0 max</div>
</div>
:::

---

## Market Signal Dashboard

*Live indicators as of September 21, 2026, used to calibrate allocation decisions.*

```{r signal-table}
signal_colors <- c(
  "attractive"   = "#d4edda",
  "neutral"      = "#f8f9fa",
  "neutral_usd"  = "#f8f9fa",
  "moderate"     = "#fff3cd",
  "caution"      = "#f8d7da"
)
signal_labels <- c(
  "attractive"   = "✓ Attractive",
  "neutral"      = "Neutral",
  "neutral_usd"  = "Neutral",
  "moderate"     = "⚠ Moderate",
  "caution"      = "✗ Caution"
)

signals |>
  mutate(
    signal_label = signal_labels[signal],
    bg           = signal_colors[signal]
  ) |>
  select(Indicator = indicator,
         `Current Reading` = raw_value,
         Signal = signal_label,
         Implication = implication) |>
  gt() |>
  tab_header(
    title    = "Market Signal Dashboard",
    subtitle = "Indicator-driven modifiers applied to conviction scores"
  ) |>
  tab_style(
    style     = cell_fill(color = signal_colors["attractive"]),
    locations = cells_body(rows = Signal == "✓ Attractive")
  ) |>
  tab_style(
    style     = cell_fill(color = signal_colors["moderate"]),
    locations = cells_body(rows = Signal == "⚠ Moderate")
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_body(columns = Signal, rows = Signal == "✓ Attractive")
  ) |>
  cols_width(Indicator ~ px(200), `Current Reading` ~ px(160),
             Signal ~ px(110), Implication ~ px(280)) |>
  opt_row_striping(row_striping = FALSE) |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

**Key takeaway:** All momentum signals are currently neutral, meaning no major near-term catalysts
are reinforcing or reversing the baseline conviction scores. The one standout signal is
**Colombia TES real yield at 5.7%** (Fisher-adjusted) — classified as Attractive. This supports
prioritizing COP assets in the near term while the USD/COP rebalancing gap is closed.

---

## Allocation Roadmap

The plan runs in two sequential phases. Phase 1 addresses the currency imbalance; Phase 2 builds
the long-run global portfolio.

<div class="phase-header">Phase 1 — COP Reserve Build (Now through ~Jan 2027, ~3-4 months)</div>

**All $5,200/month goes to Colombian COP-denominated income assets** until the spending-based
reserve is funded (~$19,600 target across 2 institutions). This is a liability hedge, not a yield
play. No new USD equity or bond positions during this phase.

Priority order for COP contributions:

```{r cop-phase1-table}
cop_rank |>
  filter(vehicle_type %in% c("cdt", "government_bond")) |>
  arrange(desc(cop_score)) |>
  head(6) |>
  mutate(
    fogafin_label = if_else(fogafin_guaranteed, "✓ Yes", "No"),
    vehicle_type  = case_when(
      vehicle_type == "cdt"             ~ "Bank CDT",
      vehicle_type == "government_bond" ~ "Sovereign Bond",
      TRUE                              ~ vehicle_type
    )
  ) |>
  select(
    Vehicle         = vehicle_name,
    Type            = vehicle_type,
    `Nominal (%)` = nominal_yield_pct,
    `Real COP (%)` = real_yield_pct,
    Risk            = risk_level,
    `Fogafin`       = fogafin_label,
    Score           = cop_score
  ) |>
  mutate(across(where(is.numeric), ~ round(., 1))) |>
  gt() |>
  tab_header(title = "Phase 1 COP Vehicle Priority — Ranked by Score") |>
  data_color(
    columns = `Real COP (%)`,
    fn      = col_numeric(
      palette = c("#f5f5f5", CLR_GREEN),
      domain  = c(3, 8)
    )
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_body(rows = 1)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

::: note-box
**Recommended Phase 1 COP allocation:**  
- **BBVA CDT 360 Days** — 10.5% nominal / 4.7% real. Fogafin-insured up to 50M COP. Start here.  
- **Bancolombia CDT 360 Days** — 10.2% nominal / 4.5% real. Same insurance. Diversifies bank exposure.  
- **TES Colombia 5-Year** — 11.2% nominal / 5.4% real. Sovereign; no deposit insurance needed. Add once CDT limits approached.
:::

<div class="phase-header">Phase 2 — 7-Class Global Portfolio (After COP gap is closed)</div>

Resume the $5,200/month in USD-denominated assets, deployed across the target allocation.
Rebalance existing holdings toward these targets as well.

```{r phase2-allocation-table}
investable <- 309908 + 39847  # current investable base

tibble(
  `Asset Class`    = c("U.S. Large Cap", "International Developed", "Emerging Markets",
                        "Bonds / Ladder", "Infrastructure", "Commodities / Transition",
                        "Cash Reserve"),
  Vehicle          = c("SPY or VTI", "VEA", "VWO or INDA",
                       "VBTLX or bond ladder", "GRID", "COPX or URA", "HYSA / Money Market"),
  `Target %`       = c(20, 15, 15, 25, 10, 5, 10),
  `Target $ (now)` = round(c(20, 15, 15, 25, 10, 5, 10) / 100 * investable),
  `Monthly $ DCA`  = round(c(20, 15, 15, 25, 10, 5, 10) / 100 * 5200)
) |>
  gt() |>
  tab_header(
    title    = "Phase 2 Target Allocation",
    subtitle = paste0("Investable base ≈ $",
                      format(round(investable / 1000), big.mark = ","), "K  |  ",
                      "Monthly DCA = $5,200")
  ) |>
  fmt_currency(columns = c(`Target $ (now)`, `Monthly $ DCA`), decimals = 0) |>
  fmt_percent(columns = `Target %`, scale_values = FALSE, decimals = 0) |>
  grand_summary_rows(
    columns  = c(`Target %`, `Target $ (now)`, `Monthly $ DCA`),
    fns      = list(label = "Total", fn = "sum"),
    fmt      = list(
      ~ fmt_percent(., columns = `Target %`, scale_values = FALSE, decimals = 0),
      ~ fmt_currency(., columns = `Target $ (now)`, decimals = 0),
      ~ fmt_currency(., columns = `Monthly $ DCA`, decimals = 0)
    )
  ) |>
  tab_style(
    style     = list(cell_fill(color = "#f0f7f4"), cell_text(weight = "bold")),
    locations = cells_grand_summary()
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

---

## Global ETF Rankings

*Conviction scores (0–5) reflect a composite of valuation, macro tailwind, catalyst strength,
implementation quality, and risk control — then adjusted by live indicator signals.*

```{r etf-chart}
top_etfs <- alloc |>
  arrange(desc(adjusted_score)) |>
  head(12) |>
  mutate(
    label    = paste0(symbol, "\n", country_or_region),
    label    = factor(label, levels = rev(label)),
    category = case_when(
      category == "Country ETF"     ~ "Country",
      category == "Benchmark"       ~ "Benchmark",
      category == "Infrastructure"  ~ "Infrastructure",
      category == "Commodity theme" ~ "Commodity",
      TRUE                          ~ category
    ),
    bar_color = case_when(
      category == "Country"        ~ CLR_NAVY,
      category == "Infrastructure" ~ CLR_GREEN,
      category == "Commodity"      ~ CLR_AMBER,
      TRUE                         ~ CLR_GRAY
    )
  )

top_etfs |>
  ggplot(aes(x = adjusted_score, y = label, fill = bar_color)) +
  geom_col(width = 0.65) +
  geom_text(
    aes(label = sprintf("%.2f", adjusted_score)),
    hjust = -0.15, size = 3.3, color = "#333"
  ) +
  scale_fill_identity() +
  scale_x_continuous(
    limits = c(0, 5.2),
    expand = expansion(mult = c(0, 0))
  ) +
  labs(
    title    = "Top ETFs by Conviction Score (Indicator-Adjusted)",
    subtitle = paste0("Score 0–5  |  ",
                      "Navy = Country ETF  |  Green = Infrastructure  |  Amber = Commodity"),
    x = "Conviction Score", y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor   = element_blank())
```

```{r etf-detail-table}
alloc |>
  arrange(desc(adjusted_score)) |>
  head(10) |>
  mutate(
    annualized_return     = percent(annualized_return, accuracy = 0.1),
    annualized_volatility = percent(annualized_volatility, accuracy = 0.1),
    max_drawdown          = percent(max_drawdown, accuracy = 0.1),
    sharpe_proxy          = round(sharpe_proxy, 2),
    adjusted_score        = round(adjusted_score, 2)
  ) |>
  select(
    Symbol     = symbol,
    Region     = country_or_region,
    `Ann. Return` = annualized_return,
    `Volatility`  = annualized_volatility,
    `Max Drawdown`= max_drawdown,
    `Sharpe`      = sharpe_proxy,
    `Score`       = adjusted_score
  ) |>
  gt() |>
  tab_header(title = "Top 10 ETFs — Key Metrics") |>
  data_color(
    columns = Score,
    fn      = col_numeric(palette = c("#f5f5f5", CLR_NAVY), domain = c(2.5, 5))
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_body(rows = 1)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

---

## COP Investment Vehicles

*All yields shown are for a USD-based investor holding COP assets. Real COP yield uses the
Fisher equation (nominal – inflation / 1 + inflation) with Colombia CPI ~5.5%. FX-adjusted
yields assume COP/USD movement under three scenarios.*

```{r cop-full-table}
cop_rank |>
  arrange(desc(cop_score)) |>
  mutate(
    fogafin_label = if_else(fogafin_guaranteed, "✓", "–"),
    vehicle_type  = case_when(
      vehicle_type == "cdt"             ~ "Bank CDT",
      vehicle_type == "government_bond" ~ "Gov. Bond",
      vehicle_type == "corporate_bond"  ~ "Corp. Bond",
      vehicle_type == "savings"         ~ "Savings",
      TRUE                              ~ vehicle_type
    )
  ) |>
  select(
    Vehicle   = vehicle_name,
    Type      = vehicle_type,
    `Nominal (%)` = nominal_yield_pct,
    `Real COP (%)` = real_yield_pct,
    Risk      = risk_level,
    Fogafin   = fogafin_label,
    Score     = cop_score
  ) |>
  mutate(across(where(is.numeric), ~ round(., 1))) |>
  gt() |>
  tab_header(
    title    = "COP Investment Vehicle Comparison",
    subtitle = "Ranked by composite score (real yield + risk + liquidity + insurance)"
  ) |>
  data_color(
    columns = `Real COP (%)`,
    fn      = col_numeric(
      palette = c("#f5f5f5", CLR_GREEN),
      domain  = c(0, 8)
    )
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_body(rows = Score >= 2.7)
  ) |>
  tab_style(
    style     = cell_text(color = CLR_GRAY),
    locations = cells_body(rows = Score < 1)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

---

## Investment Rationale

### Why COP Assets First?

The family incurs recurring COP-denominated costs (~$231/month fixed, plus ~$858/month during
Colombia visits) regardless of currency performance. Wife Anna is a Colombian citizen and the
family spends ~1-3 months per year in Colombia. The Colombian home (~$375K USD) is a legacy
asset for son Anton and is not investable. The hedge needs to come from *income-generating* COP
assets sized to cover spending needs.

The goal is a **spending-based COP reserve** (~$19,600 USD / ~62M COP) covering 18 months of
Colombia-linked costs across two Fogafin-insured institutions. This is a liability-matching
strategy, not a yield play. After full U.S. and Colombian tax accounting, CDTs do not outperform
USD T-bills in dollar terms; their value is spending-coverage certainty without requiring
ongoing USD-to-COP conversions.

Colombia's current rate environment makes CDTs an effective reserve vehicle:

- **CDT deposits at BBVA/Bancolombia** yield 10.2–10.5% nominal. After Colombian withholding
  (~7%) and U.S. tax (net of FTC), real COP yield is approximately 2.3% — modest, but the
  instrument serves as a spending hedge, not a return driver.
- **TES Colombia (direct only):** 11.2% nominal / ~5.4% real. Sovereign, no deposit cap.
  Purchasable through Valores Bancolombia only. Do not use FICs or fiducias (PFIC risk).
- Fogafin insurance caps at 50M COP per institution (~$15,625 USD). The 18-month base reserve
  requires 2 institutions to stay within insured limits.

**The ~4-month COP reserve build does not require a view that COP will appreciate.**
Once funded, all contributions shift to the 7-class USD global portfolio.

### Why INDA (India)?

**Conviction: 3.75 / 5.0** — Highest in the country ETF universe.

India is the fastest-growing major economy globally and the only country with a credible
multi-decade demographic tailwind. Key drivers:

- Working-age population growing through 2045 (China and Europe are contracting)
- Manufacturing supply chain diversification from China ("China+1" strategy)
- Domestic consumption story largely independent of global trade cycle
- Reforms: GST implementation, digital public infrastructure, startup ecosystem
- Valuation premium vs. EM peers is real but partially justified by growth differential

**Risk:** India is not cheap on absolute P/E. A global risk-off selloff hits Indian equities hard.
Currency (INR/USD) adds volatility. Watch: current account deficit, inflation persistence, BJP
policy continuity.

### Why VWO (Emerging Markets Broad)?

**Conviction: 3.72 / 5.0**

EM broadly trades at a significant P/E discount to the S&P 500 (~12x vs ~21x). The basket
provides diversification across India, Taiwan (semiconductors), China (selective recovery exposure),
Brazil (commodity link), and South Korea. VWO is liquid, low-cost, and provides instant EM breadth.

**Risk:** China is the largest single country weight (~25% of VWO); geopolitical escalation
around Taiwan would hit VWO hardest. USD strength is a structural headwind to EM returns.

### Why EWJ (Japan)?

**Conviction: 3.61 / 5.0**

Japan is the most interesting developed market value story in a decade:

- **Corporate governance reform** (TSE pressure to raise ROE and return cash to shareholders)
  is a structural catalyst unlike previous "Japan is cheap" cycles
- **Yen undervaluation** is at multi-decade extremes; mean reversion provides FX tailwind for
  USD investors even at flat local equity prices
- Warren Buffett's Berkshire Hathaway holding large positions in Japanese trading houses validates
  the deep value thesis from a credible source
- Domestic inflation is returning after 30 years, supporting nominal earnings growth

**Risk:** BOJ rate normalization can tighten financial conditions; yen appreciation helps USD
returns but can pressure export-heavy earnings domestically.

### Why GRID (Electric Grid Infrastructure)?

**Conviction: Leading theme ETF by macro tailwind (4.0) and catalyst strength (3.8)**

The global electricity grid requires an estimated $20+ trillion in investment through 2050.
GRID gives exposure to companies building transmission, distribution, and grid modernization
infrastructure across the U.S., Europe, and Asia. This theme is:

- **Policy-driven** (IRA in U.S., Green Deal in Europe, India grid expansion)
- **Geopolitically resilient** — grid investment is a domestic priority in every major economy
- **Earnings visible** — utility-style regulated returns with growth optionality

**Risk:** Interest rate sensitivity (infrastructure companies carry significant debt). GRID is
more volatile than a pure utility ETF. Regulatory risk in European markets.

### Why not U.S. Large Cap as the core position?

The S&P 500 is not excluded — it remains 20% of the Phase 2 target. However, the starting
position is effectively 89% cash/liquid (which shadows USD performance). The marginal
investment dollar adds more diversification and return potential in non-U.S. assets at
current valuations. U.S. large cap will be built systematically in Phase 2 via SPY/VTI.

---

## Risks and Falsification

```{r risk-table}
tibble(
  Risk = c(
    "COP/USD depreciation",
    "Colombia political instability",
    "U.S. recession / global risk-off",
    "India equity correction",
    "BOJ rate shock (Japan)",
    "Sustained high U.S. inflation",
    "Spending significantly exceeds $8,315/mo",
    "Unexpected large health expenditure"
  ),
  Probability = c("Medium", "Medium", "Medium", "Low–Med",
                  "Low–Med", "Low", "Medium", "Low"),
  Impact = c("Low–Med", "High", "Medium", "Medium",
             "Low–Med", "Medium", "High", "High"),
  Mitigation = c(
    "COP assets earn 10%+ nominal; FX loss must exceed yield to lose money in USD terms",
    "TES bonds are sovereign; CDTs have Fogafin insurance. Diversify across instrument types",
    "Guaranteed income ($7,488/mo) covers most spending; liquid reserve absorbs the rest",
    "INDA position built via DCA over months; position sizing limits single-country risk",
    "BOJ moves are telegraphed; EWJ position is modest within portfolio",
    "U.S. TIPS or I-bonds can hedge; bond ladder shortens duration in high inflation",
    "Liquid reserve ($310K) provides 37+ months of runway; monitor monthly",
    "VA + Medicare provide primary coverage; Colombian Medicina Prepagada adds backup"
  )
) |>
  gt() |>
  tab_header(title = "Key Risks and Mitigations") |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = Impact == "High")
  ) |>
  cols_width(
    Risk ~ px(220), Probability ~ px(100),
    Impact ~ px(90), Mitigation ~ px(340)
  ) |>
  opt_row_striping(row_striping = FALSE) |>
  tab_options(table.font.size = 12.5, table.width = pct(100))
```

### What Would Falsify This Plan?

The following would trigger a material revision of the investment approach:

1. **Colombia macro deterioration:** Policy rate cut below 8%, inflation re-accelerating above 8%, or
   material sovereign credit rating downgrade → reduce COP allocation and shorten durations.
2. **COP depreciation > 15% in 12 months:** The FX-adjusted yield becomes negative on CDTs. Pause
   new COP contributions; hold existing until maturity.
3. **U.S. recession confirmed** (two negative GDP quarters): De-risk equity exposure; extend bond
   ladder; increase cash reserve target to 15–20%.
4. **Monthly spending sustainably > $10,000:** Liquid runway shortens below 24 months; pause
   investment contributions and rebuild reserve first.
5. **India P/E > 30x on forward earnings with no growth acceleration:** Trim INDA; rotate to
   cheaper EM or increase VWO weighting.

---

## Quarterly Review Checklist

At the start of each quarter (January, April, July, October), run:

```r
source("scripts/00_quarterly_refresh.R")
```

This script automatically:

1. Refreshes ETF price data (48 tickers)
2. Regenerates global conviction scores
3. Runs the live indicator pipeline and updates allocation recommendations
4. Renders the monthly allocation brief to HTML

Then complete the manual checklist the script prints:

- Export latest Banktivity accounts as QIF → run `scripts/04_quarterly_wealth_dashboard.R`
- Run `scripts/06_colombia_economic_snapshot.R` and verify COP/USD rate
- Run `scripts/07_evaluate_colombia_investments.R` — check CDT rate quotes
- Run `scripts/08_quarterly_dual_currency_review.R` — update COP home value if needed
- Review `outputs/tables/` for any change in top ETFs or COP vehicle rankings
- Commit results to git

---

> **Disclaimer:** This is research and analysis only, not personalized financial advice. Consult a
> qualified financial advisor before making investment decisions. Past performance of referenced
> ETFs and securities does not guarantee future results. Yields and valuations are as of
> September 21, 2026, and will change.
