---
title: "Financial Snapshot"
subtitle: "Personal Wealth Overview — September 2026"
date: today
format:
  html:
    theme: cosmo
    embed-resources: true
    toc: true
    toc-depth: 2
    toc-title: "On This Page"
    fig-width: 9
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(gt)
library(scales)

# ── Data ──────────────────────────────────────────────────────────────────────
# Always load the most recently dated snapshot. These files come from the
# Banktivity QIF import (scripts/04_quarterly_wealth_dashboard.R) and only
# change when a new QIF export is processed.
latest_file <- function(dir, pattern) {
  f <- list.files(dir, pattern = pattern, full.names = TRUE) |> sort(decreasing = TRUE)
  if (length(f) == 0) stop("No file found matching '", pattern, "' in ", dir)
  f[1]
}

accounts    <- read_csv(latest_file("data/processed", "^\\d{4}-\\d{2}-\\d{2}_accounts_from_banktivity\\.csv$"),
                        show_col_types = FALSE)
spending    <- read_csv(latest_file("data/processed", "^\\d{4}-\\d{2}-\\d{2}_spending_by_category\\.csv$"),
                        show_col_types = FALSE)
nw_stmt     <- read_csv(latest_file("data/processed", "^\\d{4}-\\d{2}-\\d{2}_net_worth_statement\\.csv$"),
                        show_col_types = FALSE) |> filter(!is.na(balance))
large_items <- read_csv(latest_file("data/processed", "^\\d{4}-\\d{2}-\\d{2}_large_one_time_items\\.csv$"),
                        show_col_types = FALSE)

# ── Constants ─────────────────────────────────────────────────────────────────
MONTHLY_INCOME  <- 7488          # SS $3,100 + VA Disability $4,388
MONTHLY_SPEND   <- 8315          # 12-month recurring average
NET_FLOW        <- MONTHLY_INCOME - MONTHLY_SPEND   # –$827
ANNUAL_FLOW     <- NET_FLOW * 12                    # –$9,924
USD_NW          <- 700715        # updated Sep 23, 2026 from new Banktivity export
COP_HOME_USD    <- 375000        # 1.2B COP ÷ 3,200 COP/USD — unchanged
COP_BANK_USD    <-   9375        # 30M COP ÷ 3,200 COP/USD — unchanged
COMBINED_NW     <- USD_NW + COP_HOME_USD + COP_BANK_USD
LIQUID_RESERVE  <- 162709        # non-IRA liquid: WF Cash $153,492 + checking ~$9,217; MassMutual IRA excluded (locked until Oct 2027)

# ── Palette ───────────────────────────────────────────────────────────────────
CLR_NAVY  <- "#1e3a5f"
CLR_GREEN <- "#4a9e7a"
CLR_AMBER <- "#c97d25"
CLR_RED   <- "#c94040"
CLR_GRAY  <- "#6c757d"
```

```{=html}
<style>
.kpi-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(175px, 1fr));
  gap: 1rem;
  margin: 0.5rem 0 2.5rem 0;
}
.kpi-card {
  background: #f8f9fa;
  border-left: 4px solid #1e3a5f;
  border-radius: 6px;
  padding: 1.1rem 1.3rem 0.9rem;
}
.kpi-value {
  font-size: 1.65rem;
  font-weight: 700;
  color: #1e3a5f;
  line-height: 1.1;
}
.kpi-label {
  font-size: 0.72rem;
  color: #6c757d;
  text-transform: uppercase;
  letter-spacing: 0.06em;
  margin-top: 0.3rem;
}
.kpi-sub {
  font-size: 0.78rem;
  color: #adb5bd;
  margin-top: 0.2rem;
}
.kpi-card.green  { border-left-color: #4a9e7a; }
.kpi-card.green  .kpi-value { color: #4a9e7a; }
.kpi-card.amber  { border-left-color: #c97d25; }
.kpi-card.amber  .kpi-value { color: #c97d25; }
.kpi-card.red    { border-left-color: #c94040; }
.kpi-card.red    .kpi-value { color: #c94040; }
.note-box {
  background: #f0f7f4;
  border-left: 4px solid #4a9e7a;
  border-radius: 4px;
  padding: 0.75rem 1rem;
  font-size: 0.88rem;
  color: #333;
  margin: 1rem 0;
}
.warn-box {
  background: #fff8f0;
  border-left: 4px solid #c97d25;
  border-radius: 4px;
  padding: 0.75rem 1rem;
  font-size: 0.88rem;
  color: #333;
  margin: 1rem 0;
}
hr { border-color: #dee2e6; margin: 2rem 0; }
</style>
```

## Key Metrics {.unnumbered}

::: kpi-grid
<div class="kpi-card">
<div class="kpi-value">$558K</div>
<div class="kpi-label">US Net Worth</div>
<div class="kpi-sub">As of Sep 21, 2026</div>
</div>
<div class="kpi-card green">
<div class="kpi-value">$942K</div>
<div class="kpi-label">Combined Net Worth</div>
<div class="kpi-sub">Includes Colombian assets</div>
</div>
<div class="kpi-card green">
<div class="kpi-value">$7,488</div>
<div class="kpi-label">Monthly Income</div>
<div class="kpi-sub">Guaranteed / permanent</div>
</div>
<div class="kpi-card amber">
<div class="kpi-value">$8,315</div>
<div class="kpi-label">Monthly Spending</div>
<div class="kpi-sub">12-month recurring avg</div>
</div>
<div class="kpi-card red">
<div class="kpi-value">−$827</div>
<div class="kpi-label">Net Monthly Cash Flow</div>
<div class="kpi-sub">Funded by liquid reserve</div>
</div>
<div class="kpi-card">
<div class="kpi-value">37+ mos</div>
<div class="kpi-label">Liquid Runway</div>
<div class="kpi-sub">$310K ÷ $8,315/mo</div>
</div>
:::

---

## Balance Sheet

```{r balance-sheet-table}
accounts |>
  arrange(account_category, desc(balance)) |>
  select(Account = account_name, Type = account_category, Balance = balance) |>
  gt(groupname_col = "Type") |>
  fmt_currency(columns = Balance, decimals = 0) |>
  summary_rows(
    groups = everything(),
    columns = Balance,
    fns    = list(label = "Subtotal", fn = "sum"),
    fmt    = ~ fmt_currency(., decimals = 0)
  ) |>
  grand_summary_rows(
    columns = Balance,
    fns     = list(label = "NET WORTH", fn = "sum"),
    fmt     = ~ fmt_currency(., decimals = 0)
  ) |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_row_groups()
  ) |>
  tab_style(
    style     = list(cell_fill(color = "#f0f7f4"), cell_text(weight = "bold")),
    locations = cells_grand_summary()
  ) |>
  tab_style(
    style     = cell_text(color = CLR_RED),
    locations = cells_body(columns = Balance, rows = Balance < 0)
  ) |>
  tab_header(title = "Account Balances — September 21, 2026") |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

```{r asset-breakdown-chart}
nw_stmt |>
  filter(category != "NET WORTH") |>
  mutate(
    category = factor(category, levels = rev(c(
      "Checking/Savings", "Investments", "Other Assets",
      "Credit Cards", "Other Liabilities"
    ))),
    color = if_else(balance >= 0, CLR_NAVY, CLR_RED),
    label_x = if_else(balance >= 0, balance + 3000, balance - 3000),
    hjust   = if_else(balance >= 0, 0, 1),
    label   = dollar(abs(balance), accuracy = 1, scale = 1/1000, suffix = "K")
  ) |>
  ggplot(aes(x = balance, y = category, fill = color)) +
  geom_col(width = 0.55) +
  geom_text(aes(x = label_x, label = label, hjust = hjust),
            size = 3.5, color = "#333") +
  scale_fill_identity() +
  scale_x_continuous(
    labels = dollar_format(scale = 1/1000, suffix = "K"),
    expand = expansion(mult = c(0.12, 0.18))
  ) +
  labs(title = "Assets and Liabilities Summary", x = NULL, y = NULL) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank(),
    panel.grid.minor   = element_blank(),
    axis.text.x        = element_text(color = CLR_GRAY)
  )
```

::: note-box
**Colombia assets (not in balance sheet above):** Home ≈ **$375K** (1.2B COP at 3,200 COP/USD) +
bank accounts ≈ **$9K** (30M COP). These are illiquid or abroad; the combined net worth including
them is approximately **$942K**. The investment plan focuses on building *income-generating*
COP assets (CDTs, TES bonds) rather than relying on home equity.
:::

---

## Income and Spending

```{r income-spend-chart}
tibble(
  item   = c("Social Security", "VA Disability", "Household", "Travel",
             "Dining & Restaurants", "Miscellaneous", "Groceries",
             "Electronics", "Clothing & Shoes", "Web & Internet",
             "Telephone", "Utilities", "Medical", "Other"),
  amount = c(3100, 4388, -1492, -1167, -1016, -839, -582,
             -466, -395, -395, -361, -351, -341, -910),
  type   = c("Income", "Income", rep("Spending", 12))
) |>
  mutate(
    item   = factor(item, levels = rev(item)),
    color  = if_else(type == "Income", CLR_GREEN, CLR_NAVY)
  ) |>
  ggplot(aes(x = amount, y = item, fill = color)) +
  geom_col(width = 0.65) +
  geom_vline(xintercept = 0, linewidth = 0.5, color = "#666") +
  geom_text(
    aes(
      x     = if_else(amount >= 0, amount + 60, amount - 60),
      label = dollar(abs(amount)),
      hjust = if_else(amount >= 0, 0, 1)
    ),
    size = 3.1, color = "#333"
  ) +
  scale_fill_identity() +
  scale_x_continuous(labels = dollar_format(),
                     expand = expansion(mult = c(0.18, 0.18))) +
  labs(
    title    = "Monthly Income vs Spending Breakdown",
    subtitle = "Income is guaranteed/permanent; spending is 12-month average (recurring only)",
    x = "Monthly Amount ($)", y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.minor   = element_blank())
```

::: warn-box
**Cash flow note:** Monthly income ($7,488) falls $827 short of recurring spending ($8,315).
The $5,200/month invested via Wealthfront is drawn from the $310K liquid reserve — it is
*relocation of assets*, not a cash surplus. The reserve provides 37+ months of runway at current
burn and 50+ months without the investment contributions.
:::

```{r large-items-table}
large_items |>
  filter(!is_transfer, abs(amount) >= 1000) |>
  arrange(desc(abs(amount))) |>
  head(12) |>
  mutate(Date = format(as.Date(date), "%b %d, %Y")) |>
  select(Date, Payee = payee, Category = category, Amount = amount) |>
  gt() |>
  fmt_currency(columns = Amount, decimals = 0) |>
  tab_header(
    title    = "Major One-Time Purchases",
    subtitle = "Sep 2025 – Aug 2026 (transactions > $1,000)"
  ) |>
  tab_style(
    style     = cell_text(color = CLR_RED),
    locations = cells_body(columns = Amount, rows = Amount > 0)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

*These large one-time items ($23.9K Colombia car, $9.7K Windstar cruise, $9.4K American Airlines, $6.4K Oceania cruise, $5K NuStep equipment) added ~$6,700/month on top of the recurring baseline and are not included in the $8,315/month recurring figure.*

---

## Asset Allocation

```{r allocation-chart}
investable <- 310013 + 184217  # updated Sep 23, 2026: liquid + investments = $494,230

# Wealthfront Individual Bond Ladder: $103,287 | Wealthfront Joint: $80,619
# Joint still in robo-advisor — review transfer to Fidelity/Schwab
current <- tibble(
  asset_class   = c("Bonds / Ladder", "Cash / Liquid Reserve",
                    "U.S. Large Cap", "Intl. Developed",
                    "Emerging Markets", "Infrastructure", "Commodities"),
  current_pct   = c(103287 / investable * 100,
                    310013 / investable * 100, 0, 0, 0, 0, 0),
  target_pct    = c(20, 11, 24, 18, 18, 4, 5)
)

current |>
  pivot_longer(c(current_pct, target_pct),
               names_to = "type", values_to = "pct") |>
  mutate(
    type        = if_else(type == "target_pct", "Target", "Current"),
    type        = factor(type, levels = c("Current", "Target")),
    asset_class = factor(asset_class, levels = rev(current$asset_class))
  ) |>
  ggplot(aes(x = pct, y = asset_class, fill = type)) +
  geom_col(position = "dodge", width = 0.65) +
  geom_text(
    aes(label = paste0(round(pct, 0), "%")),
    position = position_dodge(width = 0.65),
    hjust = -0.1, size = 3.2
  ) +
  scale_fill_manual(values = c("Target" = CLR_NAVY, "Current" = CLR_AMBER),
                    name = NULL) +
  scale_x_continuous(
    labels = percent_format(scale = 1),
    expand = expansion(mult = c(0, 0.15))
  ) +
  labs(
    title    = "Asset Allocation: Current vs Target",
    subtitle = paste0("Investable assets ≈ $", round(investable/1000, 0), "K  |  ",
                      "Target is the 7-class long-run allocation"),
    x = "Allocation (%)", y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.y = element_blank(),
    legend.position    = "top"
  )
```

The portfolio is currently concentrated in cash and a short bond ladder. Full deployment to the
7-class target requires a phased transition over 2–3 months (see Investment Plan for details).

---

## Currency Exposure

```{r currency-chart}
tibble(
  Scenario = rep(c("Current", "Target"), each = 2),
  Currency = rep(c("USD", "COP"), 2),
  Pct      = c(97.4, 2.6, 80.0, 20.0)
) |>
  mutate(
    Scenario = factor(Scenario, levels = c("Current", "Target")),
    Currency = factor(Currency, levels = c("COP", "USD"))
  ) |>
  ggplot(aes(x = Scenario, y = Pct, fill = Currency)) +
  geom_col(width = 0.45, position = "stack") +
  geom_text(
    aes(label = paste0(Pct, "%")),
    position  = position_stack(vjust = 0.5),
    size = 5, fontface = "bold", color = "white"
  ) +
  scale_fill_manual(values = c("USD" = CLR_NAVY, "COP" = CLR_GREEN),
                    name = "Currency") +
  scale_y_continuous(labels = percent_format(scale = 1)) +
  labs(
    title    = "Currency Allocation: Current vs Target",
    subtitle = "COP is underweight by 17.4 percentage points vs the 80/20 target",
    x = NULL, y = "Allocation (%)"
  ) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.major.x = element_blank())
```

The 80/20 USD/COP target is set to hedge currency risk while keeping the bulk of the portfolio
in the more liquid USD market. Closing the 17.4pp COP gap requires approximately $62K in
new COP-denominated income-generating investments (CDTs, TES bonds).

---

## 5-Year Net Worth Projection

*Based on $700,715 starting net worth (Sep 23, 2026 Banktivity export), –$827/month net cash flow (income minus recurring spending), and no additional one-time expenditures. Returns applied to the full investable base.*

```{r projection-chart}
nw0 <- 700715  # updated Sep 23, 2026

proj <- crossing(
  tibble(
    Scenario = c("Conservative (5%)", "Base Case (7.5%)", "Optimistic (9%)"),
    rate     = c(0.05, 0.075, 0.09),
    color    = c(CLR_AMBER, CLR_NAVY, CLR_GREEN)
  ),
  Year = 0:5
) |>
  mutate(
    # FV = PV*(1+r)^n + PMT*[(1+r)^n - 1]/r
    nw = nw0 * (1 + rate)^Year + ANNUAL_FLOW * ((1 + rate)^Year - 1) / rate,
    nw = if_else(Year == 0, nw0, nw)
  )

proj |>
  ggplot(aes(x = Year, y = nw, color = color, group = Scenario)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5) +
  geom_hline(yintercept = 500000, linetype = "dashed",
             color = CLR_GRAY, linewidth = 0.7) +
  annotate("text", x = 0.1, y = 513000,
           label = "$500K estate goal", hjust = 0,
           size = 3.2, color = CLR_GRAY) +
  geom_text(
    data = proj |> filter(Year == 5),
    aes(label = paste0(Scenario, "\n", dollar(nw, accuracy = 1, scale = 1/1000, suffix = "K"))),
    hjust = -0.05, size = 3.1
  ) +
  scale_color_identity() +
  scale_y_continuous(labels = dollar_format(scale = 1/1000, suffix = "K"),
                     expand = expansion(mult = c(0.05, 0.05))) +
  scale_x_continuous(breaks = 0:5,
                     labels = paste0("Yr ", 0:5),
                     expand = expansion(mult = c(0.02, 0.28))) +
  labs(
    title    = "5-Year Net Worth Projection (3 Scenarios)",
    subtitle = "Assumes –$9,924/year net consumption; returns on full portfolio",
    x = NULL, y = "Net Worth"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none",
        panel.grid.minor = element_blank())
```

```{r projection-table}
proj |>
  filter(Year %in% c(1, 3, 5)) |>
  select(Scenario, Year, nw) |>
  mutate(
    Year = paste0("Year ", Year),
    nw   = dollar(nw, accuracy = 1)
  ) |>
  pivot_wider(names_from = Year, values_from = nw) |>
  gt() |>
  tab_header(title = "Projected Net Worth by Scenario") |>
  tab_style(
    style     = cell_text(weight = "bold"),
    locations = cells_body(rows = Scenario == "Base Case (7.5%)")
  ) |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

All three scenarios comfortably exceed the $500K estate goal through Year 5 — growth is
driven by investment returns on the existing $558K asset base, not by new cash contributions.

---

*Data source: Banktivity QIF export (Sep 21, 2026); 12-month transaction analysis (Sep 2025–Aug 2026).
Projections are illustrative and do not guarantee future results.*

> **Disclaimer:** This is research and analysis only, not personalized financial advice. Consult a
> qualified financial advisor before making investment decisions.
