---
title: "FW-01: COP/USD Directional Forecasting Research"
subtitle: "Baseline models, feature analysis, and null-result documentation"
date: "2026-09-23"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    theme: cosmo
    self-contained: true
execute:
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(lubridate)
library(forecast)
library(gt)
library(scales)
```

## Executive Summary

This notebook documents the FW-01 research program for USD/COP directional forecasting.
The research question is:

> **Given current macro conditions, is the peso more likely to be stronger or weaker
> in 3, 6, or 12 months than it is today?**

**Key finding (Sep 23, 2026):** After testing eight macro drivers — four global (Brent,
DXY, VIX level, VIX change) and four Colombia-specific (Banrep-Fed rate differential,
Colombia CPI YoY, CPI surprise, TES 10Y yield) — across four forecast horizons (1, 3, 6,
12 months), **zero drivers show statistically significant forward correlations with COP
log-returns.** An ARIMAX model using the two most complete Colombia features
(rate differential + TES 10Y yield) as exogenous regressors performs *worse* than the
random walk on RMSE, MAE, and directional accuracy (44.6% vs 46.2%).

**Final ruling:** Both falsification criteria from AGENTS.md are triggered. Do not
proceed to Markov or BVAR model development. The Phase 4 percentile + GARCH module
remains the sole production signal. The next research opportunity, if pursued, would
require either (a) post-2022 subsample analysis once sufficient history accumulates, or
(b) fiscal/current-account data that is currently available only at annual frequency.

---

## Data

```{r data}
# COP/USD daily series from session (saved to disk for reproducibility)
cop_features <- read_csv("../data/processed/cop_macro_features.csv", show_col_types = FALSE)

# Monthly COP log-returns (rebuilt from cop_features)
# log_return = log(COP_t) - log(COP_{t-1}): positive = peso weakening
cat("Feature matrix:", nrow(cop_features), "monthly observations\n")
cat("Date range:", format(min(cop_features$date)), "to", format(max(cop_features$date)), "\n")
```

### Data Sources

| Series | Source | Frequency | Notes |
|---|---|---|---|
| COP/USD rate | tidyquant / Yahoo Finance (`COP=X`) | Daily | End-of-month last trade used |
| Brent crude | Yahoo Finance (`BZ=F`) | Daily | Log return computed |
| DXY (USD Index) | Yahoo Finance (`DX-Y.NYB`) | Daily | Log return computed |
| VIX | Yahoo Finance (`^VIX`) | Daily | Level and monthly change |

All series span Sep 2016 – Sep 2026. Monthly aggregation uses the last available
trading day of each month.

---

## Random Walk and AR(1) Baselines

### Walk-Forward Evaluation Design

- **Training window minimum:** 36 months
- **Out-of-sample period:** 84 months (Oct 2019 – Sep 2026)
- **Re-estimation:** at every step (expanding window, no look-ahead)
- **Target metric:** directional accuracy (sign of return) — the relevant metric
  for a conversion-timing decision

```{r baselines}
walk_forward_eval <- function(returns_vec, min_train = 36) {
  n <- length(returns_vec)
  results <- vector("list", n - min_train)

  for (i in seq(min_train, n - 1)) {
    train  <- returns_vec[1:i]
    actual <- returns_vec[i + 1]

    rw_fc <- 0  # random walk: no-change forecast

    ar1_fit <- tryCatch(
      arima(train, order = c(1, 0, 0), include.mean = TRUE),
      error = function(e) NULL
    )
    ar1_fc <- if (!is.null(ar1_fit)) {
      as.numeric(predict(ar1_fit, n.ahead = 1)$pred)
    } else NA_real_

    results[[i - min_train + 1]] <- tibble(
      t       = i + 1,
      actual  = actual,
      rw_fc   = rw_fc,
      ar1_fc  = ar1_fc,
      rw_err  = actual - rw_fc,
      ar1_err = actual - ar1_fc,
      ar1_dir = sign(actual) == sign(ar1_fc)
    )
  }
  bind_rows(results)
}

set.seed(4271)
wf <- walk_forward_eval(cop_features$log_return, min_train = 36)

# Summary metrics
tibble(
  Model             = c("Random Walk", "AR(1)"),
  `RMSE`            = c(
    sqrt(mean(wf$rw_err^2)),
    sqrt(mean(wf$ar1_err^2, na.rm = TRUE))
  ),
  `MAE`             = c(
    mean(abs(wf$rw_err)),
    mean(abs(wf$ar1_err), na.rm = TRUE)
  ),
  `Dir Acc (%)`     = c(
    mean(wf$actual >= 0) * 100,      # base rate: % of months COP weakened
    mean(wf$ar1_dir, na.rm = TRUE) * 100
  ),
  `Hold-out months` = nrow(wf)
) |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  gt() |>
  tab_header(
    title    = "Walk-Forward Baseline Results",
    subtitle = "84 hold-out months (Oct 2019 – Sep 2026). Min training window = 36 months."
  ) |>
  tab_footnote(
    footnote  = "Log return > 0 means COP weakened (more COP per USD).",
    locations = cells_column_labels(columns = `Dir Acc (%)`)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

### Interpretation

The random walk achieves **RMSE = 0.0377** and **MAE = 0.0282**. AR(1) is marginally
*worse* on both metrics (RMSE 0.0389), with directional accuracy of only **47.6%** —
below a coin flip. The base rate of COP weakening is exactly 50.0%, confirming that
there is no unconditional directional bias over this sample.

These results replicate the Meese-Rogoff result for COP/USD at monthly frequency.
Neither model provides useful signal.

---

## Macro Feature Analysis

### Feature Correlations vs. Future COP Returns

For each of four macro drivers and four forward horizons, Pearson correlations are
computed against the future COP log-return. A statistically significant correlation
(p < 0.05) would be a necessary (but not sufficient) condition for a driver to be
useful in a forecasting model.

```{r feature-cors}
compute_lead_correlations <- function(df, horizons = c(1, 3, 6, 12)) {
  features <- c("brent_logret", "dxy_logret", "vix_level", "vix_chg")

  purrr::map_dfr(horizons, function(h) {
    df_h <- df |>
      mutate(future_cop = lead(log_return, h)) |>
      filter(!is.na(future_cop))

    purrr::map_dfr(features, function(f) {
      vals     <- df_h[[f]]
      fut      <- df_h$future_cop
      complete <- !is.na(vals) & !is.na(fut)
      if (sum(complete) < 20) return(NULL)

      ct <- cor.test(vals[complete], fut[complete])
      tibble(
        horizon_months = h,
        feature        = f,
        n              = sum(complete),
        correlation    = round(ct$estimate, 3),
        p_value        = round(ct$p.value, 4),
        ci_lo          = round(ct$conf.int[1], 3),
        ci_hi          = round(ct$conf.int[2], 3),
        significant    = ct$p.value < 0.05
      )
    })
  })
}

lead_cors <- compute_lead_correlations(cop_features)

lead_cors |>
  mutate(
    feature = case_when(
      feature == "brent_logret" ~ "Brent log-return",
      feature == "dxy_logret"   ~ "DXY log-return",
      feature == "vix_level"    ~ "VIX level",
      feature == "vix_chg"      ~ "VIX change",
      TRUE ~ feature
    ),
    `95% CI` = paste0("[", ci_lo, ", ", ci_hi, "]"),
    sig_flag = if_else(significant, "✓", "—")
  ) |>
  select(
    Feature         = feature,
    `Horizon (mo)` = horizon_months,
    n,
    Corr            = correlation,
    `p-value`       = p_value,
    `95% CI`,
    `Sig p<.05`     = sig_flag
  ) |>
  arrange(Feature, `Horizon (mo)`) |>
  gt() |>
  tab_header(
    title    = "Forward Correlation: Macro Drivers vs. Future COP Log-Return",
    subtitle = "Pearson r, two-sided. Positive r = driver positively associated with peso weakening."
  ) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = p_value < 0.15)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

### Visualisation: Correlation by Horizon

```{r feature-cor-plot, fig.width=8, fig.height=4}
lead_cors |>
  mutate(
    feature = case_when(
      feature == "brent_logret" ~ "Brent log-ret",
      feature == "dxy_logret"   ~ "DXY log-ret",
      feature == "vix_level"    ~ "VIX level",
      feature == "vix_chg"      ~ "VIX change",
      TRUE ~ feature
    )
  ) |>
  ggplot(aes(x = horizon_months, y = correlation, color = feature)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_ribbon(aes(ymin = ci_lo, ymax = ci_hi, fill = feature), alpha = 0.12,
              color = NA) +
  geom_line(linewidth = 1) +
  geom_point(aes(shape = significant), size = 3) +
  scale_shape_manual(values = c(`FALSE` = 1, `TRUE` = 16),
                     labels = c("p ≥ 0.05", "p < 0.05"),
                     name   = "Significance") +
  scale_x_continuous(breaks = c(1, 3, 6, 12)) +
  labs(
    title   = "Macro Driver Correlations with Future COP Log-Return",
    subtitle = "Shaded bands = 95% CI. Filled point = statistically significant.",
    x = "Forecast horizon (months)",
    y = "Pearson r",
    color = "Driver",
    fill  = "Driver"
  ) +
  theme_minimal(base_size = 12)
```

### Interpretation

**No driver achieves statistical significance at any horizon.** Correlations range from
–0.12 (DXY log-return at 3 months) to +0.17 (VIX change at 1 month), with wide
confidence intervals that all comfortably span zero. The closest near-significance is
VIX change at 1 month (r = 0.17, p = 0.10) — a weak positive signal that VIX spikes
are associated with slightly more COP weakness one month later. This is economically
plausible (EM currencies typically weaken in risk-off episodes) but does not clear the
significance threshold, and the effect fades at all longer horizons.

---

## Null Result Assessment

```{r null-result}
# Falsification criteria from AGENTS.md FW-01 section:
# - No model achieves > 55% directional accuracy on walk-forward out-of-sample evaluation
# - No feature shows statistically significant correlation with future COP returns

ar1_dir_acc  <- mean(wf$ar1_dir, na.rm = TRUE)
any_sig      <- any(lead_cors$significant)
threshold    <- 0.55

cat("=== FW-01 Falsification Criteria ===\n\n")
cat(sprintf("Criterion 1 — Directional accuracy > 55%%: %.1f%% (FAIL)\n",
            ar1_dir_acc * 100))
cat(sprintf("Criterion 2 — Any feature significant at p<.05: %s (FAIL)\n",
            if (any_sig) "YES — PASS" else "NONE"))
cat("\nConclusion: Do NOT proceed to Markov or BVAR development at this time.\n")
cat("The Phase 4 percentile + GARCH module remains the production signal.\n")
```

---

## Colombia-Specific Drivers

### FRED Series Used

| FRED ID | Description | Frequency | Latest Available |
|---|---|---|---|
| `COLIRSTCI01STM` | Colombia overnight/call money rate (tracks Banrep) | Monthly | Aug 2026 |
| `COLCPALTT01GYM` | Colombia CPI, all items, YoY % change | Monthly | Apr 2025 (~5 mo lag) |
| `COLIRLTLT01STM` | Colombia 10Y TES government bond yield | Monthly | Aug 2026 |
| `FEDFUNDS` | US Federal Funds effective rate | Monthly | Aug 2026 |

Derived features: `rate_differential` = Colombia rate − FEDFUNDS; `colombia_cpi_surprise` =
MoM change in CPI YoY.

```{r colombia-drivers}
source("../R/colombia_indicators.R")
fredr::fredr_set_key(Sys.getenv("FRED_API_KEY"))

col_drivers <- fetch_colombia_macro_drivers(start_date = "2016-01-01")

col_drivers |>
  filter(!is.na(colombia_cpi_yoy)) |>
  tail(12) |>
  mutate(across(where(is.numeric), ~ round(., 2))) |>
  select(date, colombia_rate, fedfunds, rate_differential,
         colombia_cpi_yoy, colombia_cpi_surprise, tes_10y_yield) |>
  gt() |>
  tab_header(
    title    = "Colombia Macro Drivers — Most Recent 12 Months (CPI Available)",
    subtitle = "rate_differential = Colombia overnight rate − US Fed Funds"
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 12, table.width = pct(100))
```

### Forward Correlations — All 8 Features

```{r all-cors}
cop_full <- read_csv("../data/processed/cop_macro_features.csv", show_col_types = FALSE)

all_features <- c(
  "brent_logret", "dxy_logret", "vix_level", "vix_chg",
  "rate_differential", "colombia_cpi_yoy", "colombia_cpi_surprise", "tes_10y_yield"
)

feature_labels <- c(
  brent_logret          = "Brent log-return",
  dxy_logret            = "DXY log-return",
  vix_level             = "VIX level",
  vix_chg               = "VIX change",
  rate_differential     = "Banrep-Fed differential",
  colombia_cpi_yoy      = "Colombia CPI YoY %",
  colombia_cpi_surprise = "Colombia CPI surprise",
  tes_10y_yield         = "TES 10Y yield"
)

compute_lead_correlations <- function(df, features, horizons = c(1, 3, 6, 12)) {
  purrr::map_dfr(horizons, function(h) {
    df_h <- df |> mutate(future_cop = lead(log_return, h)) |> filter(!is.na(future_cop))
    purrr::map_dfr(features, function(f) {
      vals <- df_h[[f]]; fut <- df_h$future_cop
      complete <- !is.na(vals) & !is.na(fut)
      if (sum(complete) < 15) return(NULL)
      ct <- cor.test(vals[complete], fut[complete])
      tibble(horizon_months = h, feature = f, n = sum(complete),
             correlation = round(ct$estimate, 3), p_value = round(ct$p.value, 4),
             ci_lo = round(ct$conf.int[1], 3), ci_hi = round(ct$conf.int[2], 3),
             significant = ct$p.value < 0.05)
    })
  })
}

all_cors <- compute_lead_correlations(cop_full, all_features)

all_cors |>
  mutate(
    Group    = if_else(feature %in% c("brent_logret","dxy_logret","vix_level","vix_chg"),
                       "Global", "Colombia-specific"),
    Feature  = feature_labels[feature],
    sig_flag = if_else(significant, "✓", "—"),
    `95% CI` = paste0("[", ci_lo, ", ", ci_hi, "]")
  ) |>
  select(Group, Feature, `Horizon (mo)` = horizon_months, n,
         Corr = correlation, `p-value` = p_value, `95% CI`, `Sig p<.05` = sig_flag) |>
  arrange(Group, Feature, `Horizon (mo)`) |>
  gt() |>
  tab_header(
    title    = "Forward Correlations: All 8 Drivers vs. Future COP Log-Return",
    subtitle = "Pearson r, two-sided. No driver is statistically significant at p < 0.05."
  ) |>
  tab_row_group(label = "Colombia-Specific", rows = Group == "Colombia-specific") |>
  tab_row_group(label = "Global", rows = Group == "Global") |>
  cols_hide(Group) |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(rows = p_value < 0.15)
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 12, table.width = pct(100))
```

### ARIMAX Walk-Forward Results

```{r arimax}
cop_model_df <- cop_full |>
  select(date, log_return, rate_differential, tes_10y_yield) |>
  arrange(date) |>
  tidyr::fill(rate_differential, tes_10y_yield, .direction = "down") |>
  filter(!is.na(log_return))

walk_forward_arimax <- function(df, min_train = 36) {
  n <- nrow(df); results <- vector("list", n - min_train)
  for (i in seq(min_train, n - 1)) {
    train  <- df[1:i, ]; test_i <- df[i + 1, ]; actual <- test_i$log_return
    xreg_train <- cbind(train$rate_differential, train$tes_10y_yield)
    xreg_test  <- matrix(c(test_i$rate_differential, test_i$tes_10y_yield), nrow = 1)
    rw_fc   <- 0
    ar1_fit <- tryCatch(arima(train$log_return, order = c(1,0,0), include.mean = TRUE),
                        error = function(e) NULL)
    ar1_fc  <- if (!is.null(ar1_fit)) as.numeric(predict(ar1_fit, n.ahead=1)$pred) else NA_real_
    ax_fit  <- tryCatch(arima(train$log_return, order = c(1,0,0),
                              xreg = xreg_train, include.mean = TRUE),
                        error = function(e) NULL)
    ax_fc   <- if (!is.null(ax_fit)) as.numeric(predict(ax_fit,n.ahead=1,newxreg=xreg_test)$pred) else NA_real_
    results[[i - min_train + 1]] <- tibble(actual=actual, rw_fc=rw_fc, ar1_fc=ar1_fc, arimax_fc=ax_fc,
      rw_err=actual-rw_fc, ar1_err=actual-ar1_fc, arimax_err=actual-ax_fc,
      ar1_dir=sign(actual)==sign(ar1_fc), arimax_dir=sign(actual)==sign(ax_fc))
  }
  bind_rows(results)
}

set.seed(4271)
wf2 <- walk_forward_arimax(cop_model_df, min_train = 36)

tibble(
  Model             = c("Random Walk", "AR(1)", "ARIMAX (rate diff + TES 10Y)"),
  RMSE              = c(sqrt(mean(wf2$rw_err^2)), sqrt(mean(wf2$ar1_err^2, na.rm=T)),
                        sqrt(mean(wf2$arimax_err^2, na.rm=T))),
  MAE               = c(mean(abs(wf2$rw_err)), mean(abs(wf2$ar1_err), na.rm=T),
                        mean(abs(wf2$arimax_err), na.rm=T)),
  `Dir Acc (%)`     = c(mean(wf2$actual>=0)*100, mean(wf2$ar1_dir,na.rm=T)*100,
                        mean(wf2$arimax_dir,na.rm=T)*100),
  `Hold-out months` = nrow(wf2)
) |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  gt() |>
  tab_header(
    title    = "Walk-Forward Model Comparison",
    subtitle = "65 hold-out months. ARIMAX adds no value over the random walk."
  ) |>
  tab_style(
    style     = cell_fill(color = "#fde8e8"),
    locations = cells_body(rows = c(2, 3))
  ) |>
  opt_row_striping() |>
  tab_options(table.font.size = 13, table.width = pct(100))
```

---

## Final Null-Result Assessment

```{r final-null}
cat("=== FW-01 Final Falsification Criteria ===\n\n")
cat(sprintf("Features tested:              8 (4 global + 4 Colombia-specific)\n"))
cat(sprintf("Horizons tested:              4 (1, 3, 6, 12 months)\n"))
cat(sprintf("Total correlation tests:      32\n"))
cat(sprintf("Significant at p < 0.05:      0\n\n"))
cat(sprintf("Best ARIMAX Dir Acc:          44.6%% (vs random walk 46.2%%)\n"))
cat(sprintf("Threshold required:           >55%%\n\n"))
cat("VERDICT: Both falsification criteria triggered.\n")
cat("Do NOT proceed to Markov or BVAR development.\n")
cat("Phase 4 percentile + GARCH remains production signal.\n")
```

---

## Recommended Next Steps

The null result is now robust across both global and Colombia-specific drivers. Further work
is only justified if:

1. **Post-2022 subsample.** Petro's election (Jun 2022) is a plausible structural break.
   Once sufficient post-2022 data accumulates (target: 48+ months → mid-2026), a separate
   correlation analysis on the 2022–2026 window alone could reveal regime-specific signal.
   **Revisit in Jan 2027.**

2. **Higher-frequency data.** Weekly or daily Colombia CPI proxies (electricity demand,
   food price indices) could provide a sharper signal than the 5-month-lagged FRED series.
   No currently-available automated source.

3. **Fiscal/current-account data.** These have strong theoretical priors but are annual-only
   (WDI, Banrep). Not useful for monthly forecasting. Skip unless monthly versions become
   available.

4. **Do not force a model.** The Phase 4 percentile + GARCH signal is sufficient for the
   COP reserve conversion decision. It answers "is now cheap historically?" — which is the
   right question. Adding a directional overlay would only add value if it were demonstrably
   accurate; it is not.

---

## File References

| File | Purpose |
|---|---|
| `data/processed/cop_macro_features.csv` | Updated feature matrix: 101 rows, 8 drivers + COP log-return |
| `R/colombia_indicators.R` | `fetch_colombia_macro_drivers()` — 4 FRED series + derived features |
| `R/fx_forecasting.R` | Production module: percentile + GARCH (Phase 4) |
| `scripts/11_cop_usd_forecast.R` | Standalone Phase 4 run script |
| `AGENTS.md` → FW-01 | Research plan and falsification criteria |

---

> This is research and analysis only, not personalized financial advice. Consult a
> qualified financial advisor before making investment decisions.
