---
title: "Country Investment Memo: [COUNTRY_NAME]"
subtitle: "[ETF_SYMBOL] — Global Investment Advisor"
date: today
author: "Global Investment Advisor"
format:
  html:
    theme: default
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    code-summary: "Show code"
---

# Investment Thesis

## Executive Summary

**Opportunity:** [Brief thesis statement]

**Vehicle:** [ETF symbol and name]

**Time Horizon:** [3-5 years / other]

**Benchmark:** SPY (U.S. large cap equities)

**Conviction Rating:** [HIGH / ATTRACTIVE, MONITOR / WATCHLIST / WEAK]

**Key Insight:** [What makes this compelling relative to U.S. alternatives?]

---

## Quick Snapshot

```{r setup, include=FALSE}
# Load required packages and functions
library(tidyverse)
library(tidyquant)
library(PerformanceAnalytics)
library(scales)
library(patchwork)

source(here::here("R/00_setup.R"))
source(here::here("R/indicators.R"))
source(here::here("R/plotting.R"))

# ETF symbol to analyze
ticker <- "[ETF_SYMBOL]"
benchmark <- "SPY"
analysis_start <- "2015-01-01"
```

```{r load-data, echo=FALSE, warning=FALSE}
# Load market data
prices <- tidyquant::tq_get(
  c(ticker, benchmark),
  from = analysis_start,
  to = Sys.Date(),
  get = "stock.prices"
) |>
  janitor::clean_names() |>
  dplyr::arrange(symbol, date)

returns <- prices |>
  dplyr::group_by(symbol) |>
  dplyr::arrange(date, .by_group = TRUE) |>
  dplyr::mutate(
    daily_return = adjusted / dplyr::lag(adjusted) - 1
  ) |>
  dplyr::ungroup()

# Calculate cumulative returns
cum_returns <- returns |>
  dplyr::group_by(symbol) |>
  dplyr::arrange(date, .by_group = TRUE) |>
  dplyr::mutate(
    cumulative_return = cumprod(1 + tidyr::replace_na(daily_return, 0)) - 1,
    growth_of_1 = 1 + cumulative_return
  ) |>
  dplyr::ungroup()

# Summary statistics
return_summary <- returns |>
  dplyr::group_by(symbol) |>
  dplyr::summarise(
    observations = sum(!is.na(daily_return)),
    annualized_return = mean(daily_return, na.rm = TRUE) * 252,
    annualized_volatility = sd(daily_return, na.rm = TRUE) * sqrt(252),
    sharpe_proxy = annualized_return / annualized_volatility,
    best_period = max(daily_return, na.rm = TRUE),
    worst_period = min(daily_return, na.rm = TRUE),
    .groups = "drop"
  )
```

| Metric | [COUNTRY_NAME] | SPY Benchmark | vs. SPY |
|--------|---|---|---|
| **Annualized Return** | `r percent(return_summary[return_summary$symbol == ticker, "annualized_return"][[1]], 0.1)` | `r percent(return_summary[return_summary$symbol == benchmark, "annualized_return"][[1]], 0.1)` | `r percent(return_summary[return_summary$symbol == ticker, "annualized_return"][[1]] - return_summary[return_summary$symbol == benchmark, "annualized_return"][[1]], 0.1)` |
| **Volatility** | `r percent(return_summary[return_summary$symbol == ticker, "annualized_volatility"][[1]], 0.1)` | `r percent(return_summary[return_summary$symbol == benchmark, "annualized_volatility"][[1]], 0.1)` | `r percent(return_summary[return_summary$symbol == ticker, "annualized_volatility"][[1]] - return_summary[return_summary$symbol == benchmark, "annualized_volatility"][[1]], 0.1)` |
| **Sharpe Ratio** | `r round(return_summary[return_summary$symbol == ticker, "sharpe_proxy"][[1]], 2)` | `r round(return_summary[return_summary$symbol == benchmark, "sharpe_proxy"][[1]], 2)` | – |

---

# Performance Analysis

## Growth of $1

This chart shows how $1 invested at the start of the analysis period would have grown through time.

```{r growth-plot, echo=FALSE, fig.width=10, fig.height=6}
plot_growth_of_1(
  cum_returns,
  title = paste("Growth of $1:", ticker, "vs.", benchmark),
  subtitle = paste("Since", analysis_start)
) +
  theme_gia()
```

**Key Observation:** [Describe the performance story. Is [COUNTRY] consistently beating SPY? Is there a pattern—outperformance in certain periods, underperformance in others?]

## Relative Strength

Relative strength measures performance relative to the SPY benchmark. A rising line means [COUNTRY_NAME] is outperforming; a falling line means underperforming.

```{r relative-strength, echo=FALSE, fig.width=10, fig.height=6}
# Calculate relative strength
price_wide <- prices |>
  dplyr::select(date, symbol, adjusted) |>
  tidyr::pivot_wider(names_from = symbol, values_from = adjusted)

relative_strength <- price_wide |>
  tidyr::pivot_longer(
    cols = -date,
    names_to = "symbol",
    values_to = "adjusted"
  ) |>
  dplyr::left_join(
    price_wide |>
      dplyr::select(date, benchmark_adjusted = dplyr::all_of(benchmark)),
    by = "date"
  ) |>
  dplyr::filter(symbol == ticker) |>
  dplyr::mutate(relative_strength = adjusted / benchmark_adjusted)

ggplot(relative_strength, aes(x = date, y = relative_strength)) +
  geom_line(linewidth = 0.8, color = "#2C7FB8") +
  geom_hline(yintercept = 1.0, linetype = "dashed", color = "gray60", linewidth = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  labs(
    title = paste(ticker, "Relative Strength vs.", benchmark),
    subtitle = "Above 1.0 = outperforming; below 1.0 = underperforming",
    x = NULL,
    y = "Relative Strength"
  ) +
  theme_gia()
```

**Analysis:** [Is the relative trend improving or deteriorating? What does this tell us about forward opportunity?]

## Drawdown Comparison

Understanding maximum drawdowns and recovery patterns is critical for risk assessment.

```{r drawdown-analysis, echo=FALSE, fig.width=10, fig.height=6}
# Calculate drawdowns
drawdowns <- returns |>
  dplyr::group_by(symbol) |>
  dplyr::arrange(date, .by_group = TRUE) |>
  dplyr::mutate(
    wealth_index = cumprod(1 + tidyr::replace_na(daily_return, 0)),
    prior_peak = cummax(wealth_index),
    drawdown = wealth_index / prior_peak - 1
  ) |>
  dplyr::ungroup()

plot_drawdowns(
  drawdowns,
  title = "Drawdown Comparison",
  subtitle = paste(ticker, "vs.", benchmark)
) +
  theme_gia()
```

| Metric | [COUNTRY_NAME] | SPY | Difference |
|--------|---|---|---|
| **Max Drawdown** | `r percent(min(drawdowns[drawdowns$symbol == ticker, "drawdown"][[1]], na.rm = TRUE), 0.1)` | `r percent(min(drawdowns[drawdowns$symbol == benchmark, "drawdown"][[1]], na.rm = TRUE), 0.1)` | `r percent(min(drawdowns[drawdowns$symbol == ticker, "drawdown"][[1]], na.rm = TRUE) - min(drawdowns[drawdowns$symbol == benchmark, "drawdown"][[1]], na.rm = TRUE), 0.1)` |

**Risk Assessment:** [Is [COUNTRY] more or less volatile? Does it recover faster from drawdowns? What does this mean for a U.S. investor?]

---

# Why This May Outperform the U.S.

## 1. Valuation Case

[Discuss valuation relative to U.S. equities. Are multiples cheaper? Is dividend yield higher? What does the earnings yield say?]

**Evidence:**
- [Key valuation metric 1]
- [Key valuation metric 2]
- [Key valuation metric 3]

**Conclusion:** [Is valuation attractive?]

## 2. Macro Tailwinds

[Describe the macroeconomic environment that should favor [COUNTRY_NAME]. Consider growth, inflation, monetary policy, fiscal policy, capital flows.]

### GDP and Growth

[Is real GDP growth accelerating or decelerating? How does it compare to the U.S.?]

### Inflation

[What is the inflation regime? Is it elevated or moderating? How does it compare to U.S. inflation?]

### Monetary Policy

[What is the central bank doing? Are rates rising, falling, or stable? Is this supportive or restrictive?]

### Fiscal Policy

[Is the government spending, consolidating, or in a sustainable position? Are there pro-growth policies in place?]

## 3. Currency Considerations

[Analyze the currency dynamics. Is the local currency weak (cheaper entry) or strong (better carry)?]

**USD vs. [COUNTRY_CURRENCY]:**
- Last 1 year: [direction, %]
- Last 3 years: [direction, %]
- Long-term trend: [description]

**Implication:** [Does FX help or hurt returns for a U.S. investor?]

## 4. Geopolitical Catalysts

[What geopolitical events or policy changes could catalyze outperformance?]

- **Short-term (0–12 months):** [Catalyst 1]
- **Medium-term (1–3 years):** [Catalyst 2]
- **Long-term (3+ years):** [Structural shift]

---

# Risks and What Could Go Wrong

## Bull Case Reversals

[What would invalidate this thesis? For each tailwind above, describe the opposite scenario.]

### Valuation Risk

If multiples compress further, or earnings disappoint, valuations could face pressure.

### Macro Risk

[Inflation resurges / Growth stalls / Monetary tightening / Fiscal crisis]

### Currency Risk

If the [COUNTRY_CURRENCY] strengthens sharply, returns in USD terms suffer.

### Geopolitical Risk

[Describe specific geopolitical downside scenarios: policy reversal, trade conflict, political instability, etc.]

## Historical Precedent

[Have similar setups in [COUNTRY_NAME]'s past led to disappointment? What went wrong?]

---

# Falsification Triggers

These are the levels or conditions that would convince you the thesis is wrong and should be exited:

| Trigger | Current Value | Alert Level | Implication |
|---------|---|---|---|
| **[Metric 1]** | [Value] | [Alert if < > value] | [Reason this matters] |
| **[Metric 2]** | [Value] | [Alert if < > value] | [Reason this matters] |
| **[Metric 3]** | [Value] | [Alert if < > value] | [Reason this matters] |
| **[Metric 4]** | [Value] | [Alert if < > value] | [Reason this matters] |

---

# Scenario Analysis

## Base Case (60% Probability)

[Describe the most likely scenario over your time horizon.]

**Assumed Returns:** [%]
**Key Drivers:** [List 3–4 drivers]

## Bull Case (25% Probability)

[Describe the optimistic scenario where catalysts accelerate and valuations re-rate higher.]

**Assumed Returns:** [%]
**Key Drivers:** [What has to go right?]

## Bear Case (15% Probability)

[Describe the pessimistic scenario where the thesis breaks.]

**Assumed Returns:** [%] or [negative return]
**Key Drivers:** [What has to go wrong?]

---

# Implementation & Liquidity

## ETF Details

| Attribute | Details |
|-----------|---------|
| **ETF Symbol** | [SYMBOL] |
| **Full Name** | [Full ETF Name] |
| **Manager** | [Issuer] |
| **Asset Class** | Equity |
| **Geographic Focus** | [COUNTRY] |
| **Expense Ratio** | [%] |
| **Assets Under Management** | [$B] |
| **Trading Volume (avg daily)** | [$M or # shares] |

## Liquidity Assessment

[Comment on bid-ask spreads, trading volume, and ease of entry/exit. Is this a liquid, easy-to-trade ETF or subject to wider spreads?]

## Position Sizing Recommendation

[How much of a portfolio should this represent? Is it a core holding, tactical trade, or satellite position?]

---

# Conviction Summary

**Investment Decision:** [HIGH / ATTRACTIVE, MONITOR / WATCHLIST / WEAK]

**Weighted Score Components:**
- Valuation: [1–5]
- Macro Tailwind: [1–5]
- Catalyst Strength: [1–5]
- Risk Control: [1–5]
- Implementation Quality: [1–5]

**Conviction Narrative:**

[Synthesize the bull and bear cases into a clear conviction statement. Why does this deserve [rating] conviction? What would need to change for conviction to shift up or down?]

---

# Comparison to Alternatives

How does [COUNTRY_NAME] compare to similar alternatives?

```{r comparison-table, echo=FALSE}
# Compare to similar developed or emerging market ETFs
comparison_pairs <- c(ticker, "[ALTERNATIVE_1]", "[ALTERNATIVE_2]")

comparison_data <- tidyquant::tq_get(
  comparison_pairs,
  from = analysis_start,
  to = Sys.Date(),
  get = "stock.prices"
) |>
  janitor::clean_names() |>
  dplyr::group_by(symbol) |>
  dplyr::arrange(date, .by_group = TRUE) |>
  dplyr::mutate(
    daily_return = adjusted / dplyr::lag(adjusted) - 1
  ) |>
  dplyr::ungroup() |>
  dplyr::group_by(symbol) |>
  dplyr::summarise(
    annualized_return = mean(daily_return, na.rm = TRUE) * 252,
    annualized_volatility = sd(daily_return, na.rm = TRUE) * sqrt(252),
    sharpe = annualized_return / annualized_volatility,
    .groups = "drop"
  ) |>
  dplyr::arrange(dplyr::desc(sharpe))

comparison_data |>
  gt::gt() |>
  gt::fmt_percent(columns = c(annualized_return, annualized_volatility), decimals = 1) |>
  gt::fmt_number(columns = sharpe, decimals = 2)
```

---

# Next Steps

## Due Diligence

- [ ] Review top holdings and sector exposures
- [ ] Analyze earnings growth and valuation relative to history
- [ ] Assess dividend sustainability
- [ ] Check for tax-loss harvesting opportunities
- [ ] Evaluate correlation with existing portfolio

## Monitoring Plan

- **Quarterly review:** Recheck valuation, macro, and catalyst metrics
- **Monthly check:** Monitor relative strength and drawdowns
- **Trigger review:** If any falsification trigger hits, evaluate immediately

---

# Disclaimer

This is research and analysis only, not personalized financial advice. Consult a qualified financial advisor before making investment decisions. Past performance does not guarantee future results. International investing involves currency risk, political risk, and liquidity risk. Exchange-traded funds carry their own risks, including tracking error and operational risk.

---

# Appendix: Data and Sources

**Data Sources:**
- Market prices: Yahoo Finance (via tidyquant)
- Macro data: [Sources TBD based on selected metrics]
- ETF details: ETF provider website / Morningstar

**Analysis Date:** `r Sys.Date()`

**R Session Info:**
```{r session-info, echo=FALSE}
sessionInfo()
```
