---
title: "Investment Memo: [Opportunity Name]"
subtitle: "Global Investment Advisor"
author: "Kenneth Westrick"
date: last-modified
format:
  html:
    toc: true
    toc-depth: 3
    theme: cosmo
    code-fold: true
  pdf:
    toc: true
execute:
  echo: true
  warning: false
  message: false
---

```{r}
#| label: setup

library(tidyverse)
library(tidyquant)
library(lubridate)
library(scales)
library(gt)
library(patchwork)
library(PerformanceAnalytics)
```

# Executive Summary

## Thesis

Briefly state the investment thesis in one to three paragraphs.

Template:

> [Asset, country, sector, ETF, currency, or commodity] may outperform [U.S. benchmark] over [time horizon] because [core reason]. The thesis depends on [main assumptions]. The most important risks are [key risks].

## Recommendation

| Field | Entry |
|---|---|
| Opportunity | [Name] |
| Vehicle | [ETF, ADR, equity, currency, bond, commodity, other] |
| Benchmark | [U.S. benchmark] |
| Time horizon | [Tactical / Cyclical / Strategic / Structural] |
| Conviction | [High / Medium / Low / Watchlist] |
| Primary catalyst | [Catalyst] |
| Primary risk | [Risk] |

# Research Question

State the research question clearly.

Examples:

- Is [country ETF] likely to outperform the S&P 500 over the next 12 to 36 months?
- Are [region] equities undervalued relative to U.S. equities after adjusting for growth, currency, and political risk?
- Does [commodity or sector] offer asymmetric upside compared with U.S. alternatives?

# Benchmark Comparison

Explain why the selected benchmark is appropriate.

```{r}
#| label: tickers

tickers <- c(
  opportunity = "TICKER",
  benchmark = "SPY"
)

start_date <- "2015-01-01"
```

```{r}
#| label: price-data
# eval: false

prices <- tq_get(
  tickers,
  from = start_date,
  to = Sys.Date()
)
```

```{r}
#| label: return-calculation
# eval: false

returns <- prices %>%
  group_by(symbol) %>%
  arrange(date) %>%
  mutate(daily_return = adjusted / lag(adjusted) - 1) %>%
  ungroup()
```

# Why This May Outperform the U.S.

Summarize the main reasons this opportunity could outperform.

| Driver | Evidence | Importance |
|---|---|---|
| Valuation | [Evidence] | High / Medium / Low |
| Macro backdrop | [Evidence] | High / Medium / Low |
| Currency | [Evidence] | High / Medium / Low |
| Policy | [Evidence] | High / Medium / Low |
| Capital flows | [Evidence] | High / Medium / Low |
| Geopolitics | [Evidence] | High / Medium / Low |
| Catalyst | [Evidence] | High / Medium / Low |

# Valuation

Discuss valuation relative to:

- Own history
- U.S. benchmark
- Regional peers
- Sector peers
- Expected earnings or cash-flow growth

Suggested metrics:

- P/E
- Forward P/E
- P/B
- EV/EBITDA
- Dividend yield
- Earnings yield
- Free cash-flow yield
- Real yield for bonds

# Macro Backdrop

Discuss:

- Growth
- Inflation
- Central bank policy
- Fiscal policy
- Current account
- Debt sustainability
- Credit cycle
- Capital flows

# Currency Considerations

Discuss:

- Local currency versus U.S. dollar returns
- Real effective exchange-rate valuation
- Interest-rate differentials
- Current-account support
- Inflation differentials
- Hedging availability and cost

# Geopolitical and Policy Considerations

Discuss:

- Political stability
- Policy credibility
- Conflict exposure
- Sanctions risk
- Trade exposure
- Energy security
- Reform momentum
- Regulatory risk

# Catalysts

List catalysts that could cause the market to reprice the opportunity.

| Catalyst | Expected Timing | Why It Matters |
|---|---|---|
| [Catalyst 1] | [Timing] | [Explanation] |
| [Catalyst 2] | [Timing] | [Explanation] |
| [Catalyst 3] | [Timing] | [Explanation] |

# What Could Go Wrong

State the bear case clearly.

| Risk | Mechanism | Monitoring Indicator |
|---|---|---|
| [Risk 1] | [How it hurts returns] | [Indicator] |
| [Risk 2] | [How it hurts returns] | [Indicator] |
| [Risk 3] | [How it hurts returns] | [Indicator] |

# Scenario Analysis

| Scenario | Description | Expected Outcome | Subjective Probability |
|---|---|---|---:|
| Bull | [Thesis works better than expected] | [Return or qualitative outcome] | [%] |
| Base | [Main thesis plays out] | [Return or qualitative outcome] | [%] |
| Bear | [Key assumptions fail] | [Return or qualitative outcome] | [%] |

# Falsification Triggers

The thesis should be reviewed or downgraded if:

- [Trigger 1]
- [Trigger 2]
- [Trigger 3]
- [Trigger 4]

# Implementation Notes

Discuss:

- Preferred vehicle
- Expense ratio
- Liquidity
- Bid-ask spread
- Holdings concentration
- Currency exposure
- Tax or withholding considerations
- Position sizing considerations
- Alternatives

# Conviction Rating

| Category | Score | Notes |
|---|---:|---|
| Valuation | [1-5] | [Notes] |
| Macro tailwind | [1-5] | [Notes] |
| Catalyst strength | [1-5] | [Notes] |
| Risk control | [1-5] | [Notes] |
| Implementation quality | [1-5] | [Notes] |

```{r}
#| label: conviction-score

valuation <- NA_real_
macro_tailwind <- NA_real_
catalyst_strength <- NA_real_
risk_control <- NA_real_
implementation_quality <- NA_real_

weighted_score <- valuation * 0.25 +
  macro_tailwind * 0.25 +
  catalyst_strength * 0.20 +
  risk_control * 0.15 +
  implementation_quality * 0.15

weighted_score
```

# Conclusion

State the final view in direct but conditional language.

Recommended structure:

1. Whether the opportunity is attractive relative to the U.S. benchmark.
2. What must happen for the thesis to work.
3. The most important risk.
4. What would change the conclusion.

This is research and analysis only, not personalized financial advice. Consult a qualified financial advisor before making investment decisions.
